### 2016-09-14 NOEMA/Proposal16/RXJ.tex
wording

%
% Page size and text dimensions
% Do not change!
\textheight 260mm
\textwidth 178mm
\oddsidemargin -8mm
\evensidemargin -8mm
\marginparwidth 50pt
\topmargin -22mm
\brokenpenalty=10000
\sloppy
%
%-------------------------------------------------------------------
\begin{document}
%
%
\begin{center}{\LARGE \bf
%-------------------------------------------------------------------
2-kpc scale \cco imaging of a strongly-lensed wet-merger at $z$$\sim$0.65
%-------------------------------------------------------------------
}\end{center}
\centerline{\bf P.I.: T. K. Daisy Leung}
\vspace{0.5em}
\noindent {\bf Star formation modes and molecular gas dynamics beyond the local universe} \\
\indent Tremendous progress has been made towards our understanding of the \highz
universe over the past two decades \citep[see recent reviews by][]{CW13,Madau14a, Casey14a}. These studies
suggest that the elevated \SF rates (SFRs) and specific SFRs observed in galaxies at
the peak epoch of \SF (1$\lesssim$$z$$\lesssim$3) are
primarily driven by their increased in molecular gas mass fractions and \SF efficiencies (SFEs) compared to
local galaxies, and that \SF in these early systems can be grossly categorised into
two dominant modes -- quiescent mode in disk-like galaxies versus starburst mode in commonly merger-driven
 \SB galaxies and quasar host galaxies \citep[e.g.][]{Sargent12a}. 
% brings up the spatial resolution
The systematically enhanced molecular gas fractions observed in \highz
\galpop imply that their star-forming clumps are expected to be larger in size due to 
larger internal turbulence
compared to nearby galaxies.  % Elmegreen & Elmegreen 2005, Bournaud+08
Indeed, recent studies have found gas clumps on the order of
$\sim$1$-$2\,kpc scales at $z$\ssim1--2 \citep[e.g.][]{Genzel11a, Swinbank12a, Swinbank12b}, 
% and R_{\rm 1/2} $\sim$5\,kpc disks form $\sim$1\,kpc clumps \citep{Genzel11a}, 
providing direct evidence that the
interstellar medium (ISM) conditions of galaxies evolve as a function of cosmic time. This
highlights the importance of resolving gas dynamics of galaxies on these scales 
and at various epochs in order to investigate the
mechanisms and physical processes responsible for % leading to
the two \SF modes and for causing the steep decline in the cosmic SFR density since $z$\ssim1.5 \citep[e.g.][]{Lagos11a,Popping12a}.

>>>>

%
% Page size and text dimensions
% Do not change!
\textheight 260mm
\textwidth 178mm
\oddsidemargin -8mm
\evensidemargin -8mm
\marginparwidth 50pt
\topmargin -22mm
\brokenpenalty=10000
\sloppy
%
%-------------------------------------------------------------------
\begin{document}
%
%
\begin{center}{\LARGE \bf
%-------------------------------------------------------------------
2-kpc scale \cco imaging of a strongly-lensed wet-merger at $z$$\sim$0.65
%-------------------------------------------------------------------
}\end{center}
\centerline{\bf P.I.: T. K. Daisy Leung}
\vspace{0.5em}
\noindent {\bf Star formation modes and molecular gas dynamics beyond the local universe} \\
\indent Tremendous progress has been made towards our understanding of the \highz
universe over the past two decades \citep[see recent reviews by][]{CW13,Madau14a, Casey14a}. These studies
suggest that the elevated \SF rates (SFRs) and specific SFRs observed in galaxies at
the peak epoch of \SF (1$\lesssim$$z$$\lesssim$3) are
primarily driven by their increased in molecular gas mass fractions and \SF efficiencies (SFEs) compared to
local galaxies, and that \SF in these early systems can be grossly categorised into
two dominant modes -- quiescent mode in disk-like galaxies versus starburst mode in commonly merger-driven
 \SB galaxies and quasar host galaxies \citep[e.g.][]{Sargent12a}.
% brings up the spatial resolution
The systematically enhanced molecular gas fractions observed in \highz
\galpop imply that their star-forming clumps are expected to be larger in size due to
larger internal turbulence
compared to nearby galaxies.  % Elmegreen & Elmegreen 2005, Bournaud+08
Indeed, recent studies have found gas clumps on the order of
$\sim$1$-$2\,kpc scales at $z$\ssim1--2 \citep[e.g.][]{Genzel11a, Swinbank12a, Swinbank12b},
% and R_{\rm 1/2} $\sim$5\,kpc disks form $\sim$1\,kpc clumps \citep{Genzel11a},
providing direct evidence that the
interstellar medium (ISM) conditions of galaxies evolve as a function of cosmic time. This
highlights the importance of resolving gas dynamics of galaxies on these scales
and at earlier epochs in order to investigate the
mechanisms and physical processes responsible for % leading to
the two \SF modes and for causing the steep decline in the cosmic SFR density since $z$\ssim1.5 \citep[e.g.][]{Lagos11a,Popping12a}.
